Windowed least-squares model reduction for dynamical systems

### 2019-10-16 section4/spatial_numerical.tex
bug fix
comment

\KTC{HERE} I use subscripts to denote iterations. Either is fine}

@@

Employing a linear multistep method for temporal discretization of the FOM ODE yields the FOM O$\Delta$E over the $n$th window,

>>>>

@@

Employing a linear multistep method to discretize the FOM ODE yields the FOM O$\Delta$E over the $n$th window,
\KTC{Note: the notation here is not consistent with what was defined earlier
for a discrete residual. See email.}
